---
title: "608 Module 1"
author: "Chunmei Zhu"
date: "September 2, 2018"
output: html_document
---

#Principles of Data Visualization and Introduction to ggplot2

The Data
It's about the 5,000 fastest growing companies in the US, as compiled by Inc. magazine. lets read this in:

```{r}
inc <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA_608/master/module1/Data/inc5000_data.csv", header= TRUE)

head(inc)
#colnames(inc)
#typeof(inc)
```

Preview the data

```{r}
summary(inc)
```

###Think a bit on what these summaries mean. Use the space below to add some more relevant non-visual exploratory information you think helps you understand this data:

### Insert your code here, create more chunks as necessary
```{r}
library(ggplot2)
```

Question 1
Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use. This visualization is ultimately going to be consumed on a 'portrait' oriented screen (ie taller than wide), which should further guide your layout choices.

```{r}
numOfCompanyPerState <-sort(table(inc$State),decreasing = F)

# Fitting Labels 
par(las=2) # make label text perpendicular to axis
barplot(numOfCompanyPerState,axes=FALSE,  main = "Company Distribution",horiz = TRUE, cex.names=0.4, col=c("white"))

```


Quesiton 2
Lets dig in on the state with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by companies in different industries. Create a plot that shows the average and/or median employment by industry for companies in this state (only use cases with full data, use R's complete.cases() function.) In addition to this, your graph should show how variable the ranges are, and you should deal with outliers.

```{r}
# New York is the state with the 3rd most companies
# remove two outliners with outliers of emplyees

library(dplyr)
employeeNY<-inc[complete.cases(inc),]%>%
            filter(State=="NY",Employees<1000)%>%
            select(Industry,Employees)
            

# Boxplot of the average and/or median employment by industry in NY 
boxplot(Employees~Industry,data=employeeNY, main="Employees by Industries in NY")

```

Question 3
Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart that makes this information clear. Once again, the distribution per industry should be shown.

```{r}
RevenuePerEmployee <-inc[complete.cases(inc),]%>%
                      select(Revenue,Industry,Employees)%>%
                      group_by(Industry)%>%
                      summarise(Rev_ind=sum(Revenue),Emp_ind=sum(Employees))%>%
                      mutate(Per_Revenue = Rev_ind/Emp_ind)%>%
                      arrange(desc(Per_Revenue))%>%
                      select(Industry,Per_Revenue)


p <- ggplot(RevenuePerEmployee, aes(x=Industry,y=Per_Revenue),value) +   
  stat_summary(fun.y = "sum", geom = "bar", position = "identity")

p + coord_flip()


```

